---
title: "Week 10: Quiz"
author: "Your name"
date:  "`r Sys.Date()`"
output:
  html_document:
    theme: cerulean
    highlight: tango
    toc: true
    toc_depth: 3
    toc_float: true
    self_contained: true
---
<style>

table, td, th {
  border: none;
  padding-left: 1em;
  padding-right: 1em;
  min-width: 50%;
  margin-left: auto;
  margin-right: auto;
  margin-top: 1em;
  margin-bottom: 1em;
}

</style>

```{css, echo=F}
.kakomi-box11 {
 position: relative;
 margin: 2em auto;
 padding: 1.2em;
 color: #555555; /* 文章色 */
 background-color: #fff; /* 背景色 */
 border: 1px solid #555555; /* 枠線の太さ - 色 */
 width: 90%;
}
.title-box11 {
 position: absolute;
 padding: 0 .5em;
 left: 20px;
 top: -15px;
 font-weight: bold;
 background-color: #fff; /* タイトル背景色 */
 color: #555555; /* タイトル文字色 */
}
```

```{r, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,       
  message = FALSE,      
  comment = "",
  fig.align = "center"  
  )
```

- このセクションで使う `R パッケージ`一覧    
```{r, message = FALSE}
library(tidyverse)
library(DT)
library(stargazer)
```
## 6. Excercise    
### Excercise 6.1  

- Download [hr96_21.csv](http://www.ner.takushoku-u.ac.jp/masano/class_material/waseda/keiryo/hr96_21.csv)  
- Japanese lower house election results (1996-2021)  
- Put the file (hr96_21.csv) into `data` folder in your `RProject` folder  
- Load the data and name it `hr`  

```{r}
hr <- read_csv("data/hr96-21.csv", 
               na = ".")
```
- Check the variable names in `hr`  

```{r}
names(hr)
```

-   `df1` contains the following 23 variables  

| variable| detail |
|:---------------|:-----------------------|
| year|Election year (1996-2017) |
| pref |Prefecture|
| ku |Electoral district name|
| kun  |Number of electoral district |
| rank |Ascending order of votes|
| wl | 0 = loser / 1 = single-member district (smd) winner / 2 = zombie winner|
| nocand  |Number of candidates in each district|
| seito  |Candidate's affiliated party (in Japanese)|
| j_name  | Candidate's name (Japanese)|
| name  | Candidate's name (English)|
| previous  | Previous wins|
| gender |Candidate's gender:"male", "female"|
| age  | Candidate's age|
| exp  | Election expenditure (yen) spent by each candidate |
| status|0 = challenger / 1 = incumbent / 2 = former incumbent|
| vote |votes each candidate garnered|
| voteshare  |Voteshare (%) |
| eligible  |Eligible voters in each district|
| turnout  | Turnout in each district (%)|
| castvote  | Total votes cast in each district |
| seshu_dummy  | 0 = Not-hereditary candidates, 1 = hereditary candidate|
| jiban_seshu|Relationship between candidate and his predecessor|
| nojiban_seshu |Relationship between candidate and his predecessor|
|     |    |


- Select the 2009 election data from `hr96-21.csv`, and answer the following questions.  

**Q1**: Using `seito` variable, make a party variable (DPJ dummy: `dpj`) where 民主党 = 1, others = 0.  Add `dpj` to the dataframe, `hr`, as a new variable.  

**Q2**: Using `exp` variable, make a new variable (`expm`) where the unit is not "Yen" but "million Yen". Add `expm` to the dataframe, `hr`, as a new variable.  

**Q3**: Using `status` variable, make a new variable, `inc`, where incumbent = 1, challenger and former incumbent = 0. Add `inc` to the dataframe, `hr`, as a new variable.  

**Q4**: Show the descriptive statistics of `hr` using `stargazer` package.

**Q5**: Draw a scatter plot between `expm` (x-axis) and `voteshare` (y-axis)

**Q6**: Briely explain the relationship between `expm` (x-axis) and `voteshare` (y-axis)  

**Q7**: Suppose you want to know whether campaign money (`expm`) affects votes (`voteshare`).   

○ Explanatory Variable --- `expm`  
○ Response Variable --- `voteshare`  

- Select eight control variables from the list below, run a multiple regression, and show the results using `summary()`, `tidy()`, and `stargazer` package.  
- You need to briefly explain why you think the eight control variables you select affect `voteshare.`  

| variable| detail |
|:---------------|:-----------------------|
|1. mag  |District magnitude (Number of candidate elected)|
|2. rank |Ascending order of votes|
|3. nocand  |Number of candidates in each district|
|4. j_name  | Candidate's name (Japanese)|
|5. previous  | Previous wins|
|6. gender |Candidate's gender:"male", "female"|
|7. age  | Candidate's age|
|8. wl | 0 = loser / 1 = single-member district (smd) winner / 2 = zombie winner|
|9. vote |votes each candidate garnered|
|10. eligible  |Eligible voters in each district|
|11.turnout  | Turnout in each district (%)|
|12.castvote  | Total votes cast in each district |
|13. seshu_dummy  | 0 = Not-hereditary candidates, 1 = hereditary candidate|
|14. dpj_dummy  | 0 = Not-dpj candidate, 1 = dpj candidate|
|15. inc  |challenger and former incumbent = 0, incumbent = 1|
|     |    |

**Q8**: Present your statistical results using `sjPlot` or `jtools`.   

**Q9**: Interpret the results of multiple regression analysis.  
























