---
title: "Week 6: Quiz"
author: "Your name"
date:  "`r Sys.Date()`"
output:
  html_document:
    theme: cerulean
    highlight: tango
    toc: true
    toc_depth: 3
    toc_float: true
    self_contained: true
---
 
<style>
table, td, th {
  border: none;
  padding-left: 1em;
  padding-right: 1em;
  min-width: 50%;
  margin-left: auto;
  margin-right: auto;
  margin-top: 1em;
  margin-bottom: 1em;
}
</style>
```{css, echo=F}
.kakomi-box11 {
 position: relative;
 margin: 2em auto;
 padding: 1.2em;
 color: #555555; /* 文章色 */
 background-color: #fff; /* 背景色 */
 border: 1px solid #555555; /* 枠線の太さ - 色 */
 width: 90%;
}
.title-box11 {
 position: absolute;
 padding: 0 .5em;
 left: 20px;
 top: -15px;
 font-weight: bold;
 background-color: #fff; /* タイトル背景色 */
 color: #555555; /* タイトル文字色 */
}
```
```{r, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,       
  message = FALSE,      
  comment = "",
  fig.align = "center"  
  )
```

- **このセクションで使っている `R packages`**  

```{r, comment = "", message = FALSE}

```
# 7. Exercise  
#### Q7.1:  
- Refer to `1.3 Customizing the Shape of Dots` and draw a scatter plot of 'election expenses' and 'vote percentage' in the 2009 House of Representatives election.  
- Use `shape = 23` to display a `◇` with 'yellow' inside and 'magenta' outline.

#### Q7.2:  
- Refer to `2.2 Adding Dimension by Changing Dot Colors` and draw a scatter plot of 'election expenses' and 'vote percentage' in the 2009 House of Representatives election.  
- Distinguish between candidates from the Liberal Democratic Party and others by using different colors.

#### Q7.3:  
- Refer to `2.3 Specifying Dot Colors` and draw a scatter plot of 'election expenses' and 'vote percentage' in the 2009 House of Representatives election.  
- Color the Liberal Democratic Party candidates in 'red' and all other candidates in 'grey'.

#### Q7.4:  
- Q1: Refer to `3. Scatter Plot with Regression Line (1)` and draw a scatter plot of 'election expenses' and 'vote percentage' in the 2005 House of Representatives election.  
- Use the `facet_wrap()` function to display scatter plots for each political party, ensuring that the Liberal Democratic Party and the Democratic Party are displayed next to each other.  
- Q2: Use the group_by() function to calculate the vote percentage by political party and display the results using the DT::datatable() function.

#### Q7.5:  
- Q1: Refer to `4.5 Highlighting Specific Countries` using `{gapminder}` to display a scatter plot of 'log value of GDP per capita (USD)' and 'life expectancy'.  
- Choose three countries of interest and display them in different colors.  
- Q2: Summarize concisely what can be understood from the above graph.

#### Q7.6:  
- Q1: Refer to `5.2 Adding dimensions to a scatter plot` and draw a scatter plot for the 24th (2016) House of Councillors election, with 'population density of prefectures (did)' on the x-axis and 'voting rate of 19-year-old voters (age19)' on the y-axis.  
- Apply logarithmic transformation to variables as needed.  
= Q2: Summarize concisely what can be understood from the above graph.


