---
title: "Week 4: Quiz"
author: "Your name"
date:  "`r Sys.Date()`"
output:
  html_document:
    theme: cerulean
    highlight: tango
    toc: true
    toc_depth: 3
    toc_float: true
    self_contained: true
---
<style>
 
table, td, th {
  border: none;
  padding-left: 1em;
  padding-right: 1em;
  min-width: 50%;
  margin-left: auto;
  margin-right: auto;
  margin-top: 1em;
  margin-bottom: 1em;
}

</style>

```{css, echo=F}
.kakomi-box11 {
 position: relative;
 margin: 2em auto;
 padding: 1.2em;
 color: #555555; /* 文章色 */
 background-color: #fff; /* 背景色 */
 border: 1px solid #555555; /* 枠線の太さ - 色 */
 width: 90%;
}
.title-box11 {
 position: absolute;
 padding: 0 .5em;
 left: 20px;
 top: -15px;
 font-weight: bold;
 background-color: #fff; /* タイトル背景色 */
 color: #555555; /* タイトル文字色 */
}
```

```{r, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,       
  message = FALSE,      
  comment = "",
  fig.align = "center"  
  )
```

- ここで必要な R パッケージ  

```{r}
library(tidyverse)
library(stargazer)
```  

# 8. Exercise  
## Q8.1:  

- Refer to `1. Sorting Rows: arrange()` and answer the following questions:  
- Use the House of Representatives election dataset [(hr96-21.csv)](https://asanoucla.github.io/hr96-21.csv) for the analysis.  
- Limit the displayed variables to the following six:

(1) year  
(2) ku 
(3) kun  
(4) seito  
(5) name  
(6) vote  
(7) voteshare   


- Q1: Among the candidates of the 2021 general election, list the top 10 candidates in descending order of the number of votes (`vote`) obtained.  

- Q2: Among the candidates of the 2021 general election, list the top 10 candidates in descending order of vote share (`voteshare`).  


## Q8.2:  

- Refer to `7.3 separate()` and answer the following questions:  
- Use [COVID19_Worldwide.csv](https://www.jaysong.net/RBook/Data/COVID19_Worldwide.csv) data in the analysis.  

- Q1: Draw a scatter plot for the year 2020 (January 22nd to July 10th) with `Test_Total` on the x-axis and `Confirmed_Total` on the y-axis.  
- Q2: Draw a scatter plot for the year 2020 (January 22nd to July 10th) with `Test_Total` on the x-axis and `Confirmed_Total` on the y-axis.  If there are outliers, show a scatter plot excluding them.  
