---
title: "Week 9: Quiz"
author: "Your name"
date:  "`r Sys.Date()`"
output:
  html_document:
    theme: cerulean
    highlight: tango
    toc: true
    toc_depth: 3
    toc_float: true
    self_contained: true
---
<style>

table, td, th {
  border: none;
  padding-left: 1em;
  padding-right: 1em;
  min-width: 50%;
  margin-left: auto;
  margin-right: auto;
  margin-top: 1em;
  margin-bottom: 1em;
}

</style>

```{css, echo=F}
.kakomi-box11 {
 position: relative;
 margin: 2em auto;
 padding: 1.2em;
 color: #555555; /* 文章色 */
 background-color: #fff; /* 背景色 */
 border: 1px solid #555555; /* 枠線の太さ - 色 */
 width: 90%;
}
.title-box11 {
 position: absolute;
 padding: 0 .5em;
 left: 20px;
 top: -15px;
 font-weight: bold;
 background-color: #fff; /* タイトル背景色 */
 color: #555555; /* タイトル文字色 */
}
```

```{r, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,       
  message = FALSE,      
  comment = "",
  fig.align = "center"  
  )
```

- このセクションで使う `R パッケージ`一覧    
```{r, message = FALSE}
library(tidyverse)
library(broom)
library(patchwork)
library(DT)
library(ggbeeswarm)
library(ggsignif)
library(rmarkdown)
```


# 8. Exercise    
## Exercise 8.1  
- Using the general election data [hr96-21.csv](https://asanoucla.github.io/hr96-21.csv), we want to find out if there is a difference in the average vote share of the Liberal Democratic Party (LDP) and Komeito in the 2021 general election (single-member districts).  

#### Q1:  
- Write the null hypothesis for this test.    

#### Q2:  
- Write the alternative hypothesis for this test.  

#### Q3:  
- Use the `t.test()` function to output the test result, and explain the result in simple terms.  

#### Q4: Create a boxplot + violin plot with the `geom_signif()` function to show the analysis results, including statistical significance.  

#### Q5:  
- Show the results of the t-test using a bar graph.  

#### Q6:  
- Show the results of the t-test using 'difference'.


- Download **[hr96-21.csv](http://www.ner.takushoku-u.ac.jp/masano/class_material/waseda/keiryo/Data/hr96-21.csv) **    



## Exercise 8.2  
- There is fictional data ( [menu.csv](http://https://asanoucla.github.io/menu.csv) ) where 20 respondents rated 'Cheeseburger', 'Fries', 'Teriyaki Burger', and 'Shake' at Mos Burger and McDonald's.  
- Assume that 20 respondents ate all four types of food at either Mos Burger or McDonald's.  
- The question here is "Which is tastier for the 'Cheeseburger', Mos or Mc?"  

#### Q1:  
- Write the null hypothesis for this test.  

#### Q2:  
- Write the alternative hypothesis for this test. 

#### Q3:  
- Use the `t.test()` function to output the test result, and explain the result in simple terms.  

#### Q4:  
- Create a boxplot + violin plot with the `geom_signif()` function to show the analysis results, including statistical significance.  

#### Q5:  
- Show the results of the t-test using a bar graph.  

#### Q6:  
- Show the results of the t-test using 'difference'.

- Download **[menu.csv](http://www.ner.takushoku-u.ac.jp/masano/class_material/waseda/keiryo/Data/menu.csv)**  







