---
title: "Week_13: Quiz"
author: "Your name"
date:  "`r Sys.Date()`"
output:
  html_document:
    theme: journal
    highlight: tango
    toc: true
    toc_depth: 3
    toc_float: true
    self_contained: true
---

<style>

table, td, th {
  border: none;
  padding-left: 1em;
  padding-right: 1em;
  min-width: 50%;
  margin-left: auto;
  margin-right: auto;
  margin-top: 1em;
  margin-bottom: 1em;
}

</style>

```{css, echo=F}
.kakomi-box11 {
 position: relative;
 margin: 2em auto;
 padding: 1.2em;
 color: #555555; /* 文章色 */
 background-color: #fff; /* 背景色 */
 border: 1px solid #555555; /* 枠線の太さ - 色 */
 width: 90%;
}
.title-box11 {
 position: absolute;
 padding: 0 .5em;
 left: 20px;
 top: -15px;
 font-weight: bold;
 background-color: #fff; /* タイトル背景色 */
 color: #555555; /* タイトル文字色 */
}
```

```{r, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,       
  message = FALSE,      
  comment = "",
  fig.align = "center"  
  )
```  

```{r, message = FALSE, warning = FALSE}
library(broom)
library(ggstance)
library(interplot)
library(margins)
library(msm)
library(patchwork)
library(stargazer)
library(tidyverse)
```  

# 8. Exercise  

- We want know whether the impact of campaign expenditure (`exppv`) on vote share (`voteshare`) differ as the number of winning (`previous`) for candidates in the **2012 lower house election** in Japan.  
- The 2012 lower house election is known for Prime Minister Abe's coming back to power election.  
- Data you use: [hr96_17.csv](http://www.ner.takushoku-u.ac.jp/masano/class_material/waseda/keiryo/hr96_17.csv)  
- Japanese lower house election results (1996-2017)  
- Extract the 2012 election data from `hr96-21.csv` and select the following 5 variables from this dataset and analyze them.  

| variable| detail |
|:---------------|:-----------------------|
| voteshare  |Voteshare (%) |
| exppv  | Campaign expenditure spent by each candidate per voter in their electoral district (yen) |
| age  |Candidate's age |
| nocand  |Number of candidates in each district|
| previous  |Number of candidates in each district|
|     |    |
- The variable `exppv` is not included in the dataset, so create it yourself using the two variables `exp` and `eligible` in `hr96-21.csv`.  

**Q1**: Display the descriptive statistics for the above variables.  

**Q2**: Display a scatter plot of election expenses and vote share, and briefly comment on it.  

**Q3**: Display a scatter plot of the number of times elected and vote share, and briefly comment on it.  

**Q4**: State your hypothesis regarding whether the impact of election expenses on vote share in the House of Representatives election is related to the number of times elected. Also, briefly state the reasons for your hypothesis.  

**Q5**: Display the results of the following two multiple regression analyses using the stargazer package.

```{r, eval = FALSE}
model_5 <- lm(voteshare ~ exppv*previous + age + nocand,
              data = df3)

model_6 <- lm(voteshare ~ exppv + previous + age + nocand,
              data = df3)
```  

**Q6**: Using the `interplot` package, divide the number of times elected into 13 levels from 0 to 12, and illustrate the impact of election expenses on vote share. Display the results in an easily understandable graph and describe the analysis results.

